---
title: "10-09_Corridor_comparison"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r, message=FALSE, warning=FALSE, include=FALSE}
source("../Code/merge_or_wac_with_corridor.R")
library(dplyr)
```

# Compare treatment and control corridor

## compare retail employment percentiles of each corridor in terms of Portland retail employment in general are similar or not

### calculte average retail employment for each corridor

```{r}

corridor_ave <- function(df){
  df_avg <- df %>% 
   mutate(business=CNS07+CNS18) %>% 
    summarise(CNS07_ave=mean(CNS07,na.rm=T),
            CNS18_avg=mean(CNS18,na.rm=T),
            business_avg=mean(business,na.rm=T))
  df_avg
}

corridor_list <- list(stark_oak_service,nw_everett_service,sw_alder_service)

corridor_averages <- lapply(corridor_list,corridor_ave)

corridor_averages[1]
corridor_averages[2]
corridor_averages[3]
```

### get quantiles
```{r}
# exclude blocks with no jobs in service sectors
# portland_service_no0_servic <- portland_service[apply(portland_service[,c(3:10)],1,function(x) !all(x==0)),] 

portland_service$business <- portland_service$CNS07+portland_service$CNS18

quantile(portland_service$C000,probs = seq(0, 1, by= 0.05),na.rm = T)
quantile(portland_service$CNS07,probs = seq(0, 1, by= 0.05),na.rm = T)
quantile(portland_service$CNS18,probs = seq(0, 1, by= 0.05),na.rm = T)
quantile(portland_service$business,probs = seq(0, 1, by= 0.05),na.rm = T)
```


## compare percent of retial jobs in each corridor in terms of total service jobs are similar or not
```{r}

corridor_busi_pct <- function(df){
  df_ave <- df  %>% 
  filter(year=="2010") %>% 
  mutate(business = CNS07 + CNS18) %>%
  mutate(service1 = CNS07 + CNS12 + CNS14 + CNS15 + CNS16 + CNS17 + CNS18 + CNS19) %>%
  mutate(service2 = CNS07 + CNS12 + CNS14 + CNS17 + CNS18 + CNS19) %>%
  mutate(busi_perc1 = business/service1) %>%
  mutate(busi_perc2 = business/service2)
  
  df_ave
}

corridor_busi_pct <- lapply(corridor_list,corridor_busi_pct)

t.test(corridor_busi_pct[[1]]$busi_perc1, corridor_busi_pct[[2]]$busi_perc1)
t.test(corridor_busi_pct[[1]]$busi_perc2, corridor_busi_pct[[2]]$busi_perc2)

t.test(corridor_busi_pct[[1]]$busi_perc1, corridor_busi_pct[[3]]$busi_perc1)
t.test(corridor_busi_pct[[1]]$busi_perc2, corridor_busi_pct[[3]]$busi_perc2)

```


## compare the growth rate of retial jobs are similar or not
```{r}
growth <- function(x)x/lag(x)-1
annual_grth <- function(df){
 df_grth <- df %>% 
  group_by(year) %>% 
  summarise(CNS07=sum(CNS07, na.rm=T),
          CNS18=sum(CNS18, na.rm=T),
          business=CNS07+CNS18) %>% 
  filter(!is.na(year)) %>% 
  mutate(CNS07_grth=growth(CNS07),
         CNS18_grth=growth(CNS18),
         busi_grth=growth(business))
}
  
corridor_grth <- lapply(corridor_list,annual_grth)

t.test(corridor_grth[[1]]$CNS07_grth,corridor_grth[[2]]$CNS07_grth)
t.test(corridor_grth[[1]]$CNS18_grth,corridor_grth[[2]]$CNS18_grth)
t.test(corridor_grth[[1]]$busi_grth,corridor_grth[[2]]$busi_grth)

t.test(corridor_grth[[1]]$CNS07_grth,corridor_grth[[3]]$CNS07_grth)
t.test(corridor_grth[[1]]$CNS18_grth,corridor_grth[[3]]$CNS18_grth)
t.test(corridor_grth[[1]]$busi_grth,corridor_grth[[3]]$busi_grth)


```

