---
title: "3-12_Memphis_qcew"
author: "Minji Cho"
output:
  html_document:
    df_print: paged
---

```{r}

if(!require(pacman)){install.packages("pacman"); library(pacman)}
p_load(here, RPostgreSQL, sf, ggplot2, directlabels,ggthemes, tidyverse, dplyr, dbplyr, stargazer,cowplot, lubridate, gridExtra,data.table)

#query the corridors from bike_lanes
user <- "minji2"
host <- "pgsql102.rc.pdx.edu"
pw <- scan(here::here("batteries.pgpss"), what = "")
dbname <- "bike_lanes"

con <- dbConnect("PostgreSQL", host = host, user = user, dbname = dbname, 
                 password = pw, port = 5433)

source(here::here("Code/corridor_comparison_functions.R"))

memphis_qcew <- tbl(con, "memphis_qcew") %>% collect() %>% mutate(street_group = as.character(street_group))

# exclude Jackson corridor which is not comparable to treatment corridor
memphis_qcew <- memphis_qcew[memphis_qcew$district_name!="Jackson Ave",]

memphis_qcew$Type <- as.factor(memphis_qcew$Type)

dbDisconnect(con)


# Defining function: agg_trend_table_qcew

agg_trend_table_qcew <- function(df, group) {
       df <- if(class(df) == "sf") {
       df <- as.data.frame(df, stringsAsFactors = FALSE) %>% select(-starts_with("geom"))
       } else {
       df
       }
  
       df <- df %>% filter(street_group == group)
  
df_plot <- df %>% group_by(year, Type) %>%
    summarise(emp_food = sum(emp_food),
              emp_retail = sum(emp_retail),
              wage_food = sum(wage_food),
              wage_retail = sum(wage_retail),
              estb_food = sum(estb_food),
              estb_retail = sum(estb_retail))
              
  return(df_plot)
}

```

# Trend Comparisons

## Madison Avenue

### Employment trend comparison

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width = 9.5, fig.asp=.5}

madison_agg <- agg_trend_table_qcew (memphis_qcew, group = 1)

# add a new function to draw plots with 4 control corridors
agg_trend_plot_emp <- function(df_plot, industry, corridor_name, 
                                 industry_code = c("emp_retail", "emp_food"), 
                                 construct_year, end_year) {
  
  df_plot$Type <- factor(df_plot$Type, levels = rev(levels(df_plot$Type)))
  
  #convert year to proper date
  
  df_plot$year <-as.character(paste0(df_plot$year, "-01-01"))
  df_plot$year <- as.Date(df_plot$year, "%Y-%m-%d")
  
  construct_date <- as.character(paste0(construct_year-1, "-07-01"))
  construct_date <- as.Date(construct_date, "%Y-%m-%d")
  
  end_date <- as.character(paste0(end_year-1, "-07-01"))
  end_date <- as.Date(end_date, "%Y-%m-%d")
  
  construct_date2 <- as.character(paste0(construct_year-4, "-07-01"))
  construct_date2 <- as.Date(construct_date2, "%Y-%m-%d")
  
  end_date2 <- as.character(paste0(end_year-2, "-07-01"))
  end_date2 <- as.Date(end_date2, "%Y-%m-%d")
  
  
  #making the plot
  
  ats_df <- ggplot(df_plot, aes(x = year, y = get(industry_code), 
                                group = Type, colour = Type, shape=Type)) + 
    geom_line()  +
    geom_rect(aes(xmin = as.Date(construct_date, "%Y"), 
                  xmax = as.Date(end_date, "%Y"), 
                  ymin = -Inf, ymax = Inf),
              fill = "#adff2f",linetype=0,alpha = 0.03) +
    
    geom_rect(aes(xmin = as.Date(construct_date2, "%Y"), 
                  xmax = as.Date(end_date2, "%Y"), 
                  ymin = -Inf, ymax = Inf),
              fill = "grey",linetype=0,alpha = 0.03) +
    
    geom_point(size = 3, fill="white") +
    scale_x_date(date_breaks = "2 years", date_labels = "%Y") +
    theme_minimal() +
    labs(title = glue("{industry} Employment Comparison:\n {corridor_name}"), x="Year",y="Employment",
         caption = glue("Gray shaded area is pre-construction period\n Green shaded area is construction period\n Employment is indexed to the baseline years (3 years pre-construction)")) +
    guides(title = "Street Type") 
  
  return(ats_df)
}

madison_retail_trend_plot <- agg_trend_plot_emp(madison_agg, industry = "Retail", industry_code = "emp_retail", corridor_name = "Madison Avenue", construct_year = 2011, end_year = 2012)

madison_food_trend_plot <- agg_trend_plot_emp(madison_agg, industry = "Food",industry_code = "emp_food", corridor_name = "Madision Avenue", construct_year = 2011, end_year = 2012)

prow <- plot_grid(madison_retail_trend_plot + theme(legend.position="none"),
                  madison_food_trend_plot + theme(legend.position="none"),
                  align = 'vh', hjust = -1, nrow = 1)

legend_b <- get_legend(madison_retail_trend_plot + theme(legend.position="bottom"))

plot_grid( prow, legend_b, ncol = 1, rel_heights = c(4, .2))

```

### Wage trend comparison

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width = 9.5, fig.asp=.5}

# add a new function to draw plots with 4 control corridors
agg_trend_plot_wage <- function(df_plot, industry, corridor_name, 
                                 industry_code = c("wage_retail", "wage_food"), 
                                 construct_year, end_year) {
  
  df_plot$Type <- factor(df_plot$Type, levels = rev(levels(df_plot$Type)))
  
  #convert year to proper date
  
  df_plot$year <-as.character(paste0(df_plot$year, "-01-01"))
  df_plot$year <- as.Date(df_plot$year, "%Y-%m-%d")
  
  construct_date <- as.character(paste0(construct_year-1, "-07-01"))
  construct_date <- as.Date(construct_date, "%Y-%m-%d")
  
  end_date <- as.character(paste0(end_year-1, "-07-01"))
  end_date <- as.Date(end_date, "%Y-%m-%d")
  
  construct_date2 <- as.character(paste0(construct_year-4, "-07-01"))
  construct_date2 <- as.Date(construct_date2, "%Y-%m-%d")
  
  end_date2 <- as.character(paste0(end_year-2, "-07-01"))
  end_date2 <- as.Date(end_date2, "%Y-%m-%d")

  #making the plot
  
  ats_df <- ggplot(df_plot, aes(x = year, y = get(industry_code)/1000000, 
                                group = Type, colour = Type, shape=Type)) + 
    geom_line()  +
    geom_rect(aes(xmin = as.Date(construct_date, "%Y"), 
                  xmax = as.Date(end_date, "%Y"), 
                  ymin = -Inf, ymax = Inf),
              fill = "#adff2f",linetype=0,alpha = 0.03) +
    
    geom_rect(aes(xmin = as.Date(construct_date2, "%Y"), 
                  xmax = as.Date(end_date2, "%Y"), 
                  ymin = -Inf, ymax = Inf),
              fill = "grey",linetype=0,alpha = 0.03) +
    
    geom_point(size = 3, fill="white") +
    scale_x_date(date_breaks = "2 years", date_labels = "%Y") +
    theme_minimal() +
    labs(title = glue("{industry} Wage Comparison:\n {corridor_name}"), x="Year",y="Wage (in millions)",
         caption = glue("Gray shaded area is pre-construction period\n Green shaded area is construction period\n Wage is indexed to the baseline years (3 years pre-construction)")) +
    guides(title = "Street Type") 
  
  return(ats_df)
}

madison_retail_trend_plot <- agg_trend_plot_wage(madison_agg, industry = "Retail", industry_code = "wage_retail", corridor_name = "Madison Avenue", construct_year = 2011, end_year = 2012)

madison_food_trend_plot <- agg_trend_plot_wage(madison_agg, industry = "Food",industry_code = "wage_food", corridor_name = "Madision Avenue", construct_year = 2011, end_year = 2012)

prow <- plot_grid(madison_retail_trend_plot + theme(legend.position="none"),
                  madison_food_trend_plot + theme(legend.position="none"),
                  align = 'vh', hjust = -1, nrow = 1)

legend_b <- get_legend(madison_retail_trend_plot + theme(legend.position="bottom"))

plot_grid( prow, legend_b, ncol = 1, rel_heights = c(4, .2))

```

### Establishment counts trend comparison

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width = 9.5, fig.asp=.5}

# add a new function to draw plots with 4 control corridors
agg_trend_plot_estb <- function(df_plot, industry, corridor_name, 
                                 industry_code = c("estb_retail", "estb_food"), 
                                 construct_year, end_year) {
  
  df_plot$Type <- factor(df_plot$Type, levels = rev(levels(df_plot$Type)))
  
  #convert year to proper date
  
  df_plot$year <-as.character(paste0(df_plot$year, "-01-01"))
  df_plot$year <- as.Date(df_plot$year, "%Y-%m-%d")
  
  construct_date <- as.character(paste0(construct_year-1, "-07-01"))
  construct_date <- as.Date(construct_date, "%Y-%m-%d")
  
  end_date <- as.character(paste0(end_year-1, "-07-01"))
  end_date <- as.Date(end_date, "%Y-%m-%d")
  
  construct_date2 <- as.character(paste0(construct_year-4, "-07-01"))
  construct_date2 <- as.Date(construct_date2, "%Y-%m-%d")
  
  end_date2 <- as.character(paste0(end_year-2, "-07-01"))
  end_date2 <- as.Date(end_date2, "%Y-%m-%d")


  #making the plot
  
  ats_df <- ggplot(df_plot, aes(x = year, y = get(industry_code), 
                                group = Type, colour = Type, shape=Type)) + 
    geom_line()  +
    geom_rect(aes(xmin = as.Date(construct_date, "%Y"), 
                  xmax = as.Date(end_date, "%Y"), 
                  ymin = -Inf, ymax = Inf),
              fill = "#adff2f",linetype=0,alpha = 0.03) +
    
    geom_rect(aes(xmin = as.Date(construct_date2, "%Y"), 
                  xmax = as.Date(end_date2, "%Y"), 
                  ymin = -Inf, ymax = Inf),
              fill = "grey",linetype=0,alpha = 0.03) +
    
    geom_point(size = 3, fill="white") +
    scale_x_date(date_breaks = "2 years", date_labels = "%Y") +
    theme_minimal() +
    labs(title = glue("{industry} Count Comparison:\n {corridor_name}"), x="Year",y="Number of establishments",
         caption = glue("Gray shaded area is pre-construction period\n Green shaded area is construction period\n Employment is indexed to the baseline years (3 years pre-construction)")) +
    guides(title = "Street Type") 
  
  return(ats_df)
}

madison_retail_trend_plot <- agg_trend_plot_estb(madison_agg, industry = "Retail", industry_code = "estb_retail", corridor_name = "Madison Avenue", construct_year = 2011, end_year = 2012)

madison_food_trend_plot <- agg_trend_plot_estb(madison_agg, industry = "Food",industry_code= "estb_food", corridor_name = "Madision Avenue", construct_year = 2011, end_year = 2012)

prow <- plot_grid(madison_retail_trend_plot + theme(legend.position="none"),
                  madison_food_trend_plot + theme(legend.position="none"),
                  align = 'vh', hjust = -1, nrow = 1)

legend_b <- get_legend(madison_retail_trend_plot + theme(legend.position="bottom"))

plot_grid( prow, legend_b, ncol = 1, rel_heights = c(4, .2))

```

## Broad Avenue

### Employment trend comparison

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width = 9.5, fig.asp=.5}

broad_agg <- agg_trend_table_qcew (memphis_qcew, group = 2)

broad_retail_trend_plot <- agg_trend_plot_emp(broad_agg, industry = "Retail", industry_code = "emp_retail", corridor_name = "Broad Avenue", construct_year = 2010, end_year = 2011)

broad_food_trend_plot <- agg_trend_plot_emp(broad_agg, industry = "Food",industry_code = "emp_food", corridor_name = "Broad Avenue", construct_year = 2010, end_year = 2011)

prow <- plot_grid(broad_retail_trend_plot + theme(legend.position="none"),
                  broad_food_trend_plot + theme(legend.position="none"),
                  align = 'vh', hjust = -1, nrow = 1)

legend_b <- get_legend(broad_retail_trend_plot + theme(legend.position="bottom"))

plot_grid( prow, legend_b, ncol = 1, rel_heights = c(4, .2))

```

### Wage trend comparison

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width = 9.5, fig.asp=.5}

broad_retail_trend_plot <- agg_trend_plot_wage(broad_agg, industry = "Retail", industry_code = "wage_retail", corridor_name = "Broad Avenue", construct_year = 2010, end_year = 2011)

broad_food_trend_plot <- agg_trend_plot_wage(broad_agg, industry = "Food",industry_code = "wage_food", corridor_name = "Broad Avenue", construct_year = 2010, end_year = 2011)

prow <- plot_grid(broad_retail_trend_plot + theme(legend.position="none"),
                  broad_food_trend_plot + theme(legend.position="none"),
                  align = 'vh', hjust = -1, nrow = 1)

legend_b <- get_legend(broad_retail_trend_plot + theme(legend.position="bottom"))

plot_grid( prow, legend_b, ncol = 1, rel_heights = c(4, .2))

```

### Establishment counts trend comparison

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width = 9.5, fig.asp=.5}

broad_retail_trend_plot <- agg_trend_plot_estb(broad_agg, industry = "Retail", industry_code = "estb_retail", corridor_name = "Broad Avenue", construct_year = 2010, end_year = 2011)

broad_food_trend_plot <- agg_trend_plot_estb(broad_agg, industry = "Food",industry_code= "estb_food", corridor_name = "Broad Avenue", construct_year = 2010, end_year = 2011)

prow <- plot_grid(broad_retail_trend_plot + theme(legend.position="none"),
                  broad_food_trend_plot + theme(legend.position="none"),
                  align = 'vh', hjust = -1, nrow = 1)

legend_b <- get_legend(broad_retail_trend_plot + theme(legend.position="bottom"))

plot_grid( prow, legend_b, ncol = 1, rel_heights = c(4, .2))

```

# Differences-in-Difference (DID) Analysis
```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width = 9.5, fig.asp=.5}

# Defining function: did_agg_analysis_qcew_e, did_agg_analysis_qcew_w

did_agg_analysis_qcew_e <- function(df_did, group, endyear){
  df_did <- df_did %>% filter(street_group==group) %>% 
    mutate(business=emp_food+emp_retail) %>% 
    group_by(Type, year) %>% 
    summarise(emp_retail = sum(emp_retail),
              emp_food = sum(emp_food),
              business = sum(business)) %>% 
    mutate(prepost=ifelse(as.numeric(as.character(year))>endyear,1,0))
 
  did_retail <- lm(emp_retail ~ Type + prepost + Type*prepost, data=df_did)
  did_food <- lm(emp_food ~ Type + prepost + Type*prepost, data=df_did)
  did_busi <- lm(business ~ Type + prepost + Type*prepost, data=df_did)
  
  did_final <- list(did_retail, did_food, did_busi)
  
  return(did_final)
  
  #did_retail
  #return(did_food)
  #return(did_busi)
}

did_agg_analysis_qcew_w <- function(df_did, group, endyear){
  df_did <- df_did %>% filter(street_group==group) %>% 
    mutate(business=wage_food+wage_retail) %>% 
    group_by(Type, year) %>% 
    summarise(wage_retail = sum(wage_retail),
              wage_food = sum(wage_food),
              business = sum(business)) %>% 
    mutate(prepost=ifelse(as.numeric(as.character(year))>endyear,1,0))
 
  did_retail <- lm(wage_retail ~ Type + prepost + Type*prepost, data=df_did)
  did_food <- lm(wage_food ~ Type + prepost + Type*prepost, data=df_did)
  did_busi <- lm(business ~ Type + prepost + Type*prepost, data=df_did)
  
  did_final <- list(did_retail, did_food, did_busi)
  
  return(did_final)
  
  #did_retail
  #return(did_food)
  #return(did_busi)
}

```

## Madison Ave
Three models, using retail employment, food employment and business employment/wage (sum of the previous two) as dependent variables, are estimated. The key interest term in the table is DID estimator variable, which infers the difference between treatment and control corridors.

In terms of employment, the corridor shows some mixed results depending on control corridors. In the cases of the Cooper Street and Highland Street, the difference terms for food and business employment are negative and significant. It means that the Madison Avenue treatment corridor have positive effects of infrastructure construction on the number of food and business employment. On the other hand, the difference terms for retail and business employment of the Union Avenue exhibit a statistically significant and positive effect. These results indicate that the Madison Avenue treatment corridor has negative impact on the number of retail and business employment when we use the Union Avenue as control group.

In the cases of wage, the difference terms for the Cooper Street and Highland Street are significant, while those for the Union Avenue do not show statistically significant effects. The results for the Cooper Street and Highland Street, however, are not consistent. On one hand, the difference terms for retail wage are significant and positve. On the other hand, those for food wage are significant and negative. These results indicate that the Madison Avenue treatment corridor has positive effects on the wage of food industry, while it affects wage of retail negatively. The difference terms for business, however, is not significant.

To sum up, there are different results when using the Cooper Street or Highland Street as control groups and when using the Union Avenue. Considering the trends analysis presented above, the reason why these results are derived is that the Union Avenue might be not appropriate as a control group. In short, the difference terms for the Union Avenue may not reflect the effect of a treatment excluding the effects of extraneous factors.

```{r, echo=FALSE, results='asis'}
## Reference change
memphis_qcew <- within(memphis_qcew, Type <- relevel(Type, ref="Treatment: Madison Ave"))

## DID_emp
madison_agg_did_qcew_e <- did_agg_analysis_qcew_e(memphis_qcew, group = 1, endyear = 2011)
stargazer(madison_agg_did_qcew_e[[1]], madison_agg_did_qcew_e[[2]], madison_agg_did_qcew_e[[3]], 
          title = "Madison Ave. Corridor Difference-in-Difference Estimates (Employment)", 
          column.labels  = c("Retail Emp.", "Accomodations Emp.", "'Business' Emp."), type = "html")

## DID_wage
madison_agg_did_qcew_w <- did_agg_analysis_qcew_w(memphis_qcew, group = 1, endyear = 2011)
stargazer(madison_agg_did_qcew_w[[1]], madison_agg_did_qcew_w[[2]], madison_agg_did_qcew_w[[3]], 
          title = "Madison Ave. Corridor Difference-in-Difference Estimates (Wage)", 
          column.labels  = c("Retail Wage", "Accomodations Wage", "'Business' Wage"), type = "html")

```

## Broad Ave

Three models, using retail employment, food employment and business employment/wage (sum of the previous two) as dependent variables, are estimated. The key interest term in the table is DID estimator variable, which infers the difference between treatment and control corridors.

The Broad Avenue treatment corridor shows a statistically significant and negative effects of infrastructure construction on the number of employment and wage when using the Cooper Street as a control group. When we employ the Central Avenue as a control group, however, the difference terms are not statistically significant. These inconsistent results indicate that additional analyses are necessary to identify the effects of treatment on employment and wage.

```{r, echo=FALSE, results='asis'}

## Reference change
memphis_qcew <- within(memphis_qcew, Type <- relevel(Type, ref="Treatment: Broad Ave"))

## DID_emp
broad_agg_did_qcew_e <- did_agg_analysis_qcew_e(memphis_qcew, group = 2, endyear = 2010)
stargazer(broad_agg_did_qcew_e[[1]], broad_agg_did_qcew_e[[2]], broad_agg_did_qcew_e[[3]], 
          title = "Broad Ave. Corridor Difference-in-Difference Estimates (Employment)", 
          column.labels  = c("Retail Emp.", "Accomodations Emp.", "'Business' Emp."), type = "html")

## DID_wage
broad_agg_did_qcew_w <- did_agg_analysis_qcew_w(memphis_qcew, group = 2, endyear = 2010)
stargazer(broad_agg_did_qcew_w[[1]], broad_agg_did_qcew_w[[2]], broad_agg_did_qcew_w[[3]], 
          title = "Broad Ave. Corridor Difference-in-Difference Estimates (Wage)", 
          column.labels  = c("Retail Wage.", "Accomodations Wage.", "'Business' Wage."), type = "html")

```
          
# Interrupted Time Series (ITS) Analysis
```{r}

# Defining function: agg_its_analysis_qcew_e, agg_its_analysis_qcew_w

agg_its_analysis_qcew_e <- function(df_its, group, endyear){
  df_its <- df_its %>% filter(street_group==group,street_type=="Treatment") %>% 
    mutate(business=emp_food+emp_retail) %>% 
    group_by(year) %>%
    summarise(emp_retail = sum(emp_retail),
              emp_food = sum(emp_food),
              business = sum(business)) %>% 
    mutate(prepost=ifelse(as.numeric(as.character(year))>endyear,1,0),
           ts_year=as.numeric(as.character(year))-2003)
    
  its_retail <- lm(emp_retail~ts_year + prepost + ts_year*prepost, data=df_its)
  its_food <- lm(emp_food~ts_year + prepost + ts_year*prepost, data=df_its)
  its_busi <- lm(business ~ ts_year + prepost + ts_year*prepost, data=df_its)
  
  its_final <- list(its_retail, its_food, its_busi)
  
  return(its_final)
  
}

agg_its_analysis_qcew_w <- function(df_its, group, endyear){
  df_its <- df_its %>% filter(street_group==group,street_type=="Treatment") %>% 
    mutate(business=wage_food+wage_retail) %>% 
    group_by(year) %>%
    summarise(wage_retail = sum(wage_retail),
              wage_food = sum(wage_food),
              business = sum(business)) %>% 
    mutate(prepost=ifelse(as.numeric(as.character(year))>endyear,1,0),
           ts_year=as.numeric(as.character(year))-2003)
    
  its_retail <- lm(wage_retail~ts_year + prepost + ts_year*prepost, data=df_its)
  its_food <- lm(wage_food~ts_year + prepost + ts_year*prepost, data=df_its)
  its_busi <- lm(business ~ ts_year + prepost + ts_year*prepost, data=df_its)
  
  its_final <- list(its_retail, its_food, its_busi)
  
  return(its_final)
  
}

```

## Madison Ave.

In the case of employment, *prepost* terms are significant and postivie for both retail and food, while *ts_year:prepost* coefficients are not. These results represent that the Madison Avenue corridor contributes to the increase in the level of employment for retail and food industry, although it cannot lead to significant effects on the slope changes.

In terms of wage, both *prepost* and *ts_year:prepost* terms are significant for both retail and food. In particular, *prepost* coefficients are negative and *ts_year:prepost* terms are positive. This result should be interpreted with the trend analyses because there might be misrepresentation in the estimation process. Considering both results, the treatment has a negative effect on the level of retail wage, but, at the same, it converts the slope of wage change to be positive. In other words, the treatment can contribute to the increase in retail wage in the long term, even though it makes the level of wage decrease.

In the cases of food and total business, it is infered that the treatment does not negatively affect the level of wage, although the coefficient is significant and negative. In short, the treatment has a positive effect on the slope of food wage.

```{r, echo=FALSE, results='asis'}
madison_agg_its_e <- agg_its_analysis_qcew_e(memphis_qcew, group = 1, endyear = 2011)
stargazer(madison_agg_its_e[[1]], madison_agg_its_e[[2]], madison_agg_its_e[[3]], 
          title = "Madison Ave. Corridor Interrupted Time Series Estimates (Employment)", 
          column.labels  = c("Retail Emp.", "Accomodations Emp.", "'Business' Emp."), type = "html")

madison_agg_its_w <- agg_its_analysis_qcew_w(memphis_qcew, group = 1, endyear = 2011)
stargazer(madison_agg_its_w[[1]], madison_agg_its_w[[2]], madison_agg_its_w[[3]], 
          title = "Madison Ave. Corridor Interrupted Time Series Estimates (Wage)", 
          column.labels  = c("Retail Wage", "Accomodations Wage", "'Business' Wage"), type = "html")

```

#Broad Ave.

In the case of retail employment,the *ts_year* and *prepost* coefficients are significant and positive, while the *ts_year:prepost* term is not significant. This result indicates that the Broad Avenue corridor exhibits a level change from the pre-treatment trend patterns which are an increasing pattern over time period. In terms of food and business employment, of the various coefficients, only the *prepost* terms are statistically significant and positive. This result mirrors the visual trends analyses of employments that show a clear jump after construction.

In terms of wage, the results of ITS estimates are mixed. First, the *ts_year* coefficient of retail wage is significant and positive. Others, however, are not significant. This result means that the Broad Avenue corridor does not have a significant effect on retail wage. In the case of food industry, on the other hand, all coefficients are significant. Especially, *ts_year* and *ts_year:prepost* terms are positive and *prepost* term is negative. Considering the trend of food wage, however, it is infered that the *prepost* term becomes negative in the estimation process, although treatment does not reduce the level of wage in food industry. Finally, *ts_year* and *ts_year:prepost* terms are significant and postive in terms of business wage. This result indicates that the treatment cannot lead to the change in the level of business wage, but it results in the increase in the slope of business wage change.


```{r, echo=FALSE, results='asis'}
broad_agg_its_e <- agg_its_analysis_qcew_e(memphis_qcew, group = 2, endyear = 2010)
stargazer(broad_agg_its_e[[1]], broad_agg_its_e[[2]], broad_agg_its_e[[3]], 
          title = "Broad Ave. Corridor Interrupted Time Series Estimates (Employment)", 
          column.labels  = c("Retail Emp.", "Accomodations Emp.", "'Business' Emp."), type = "html")

broad_agg_its_w <- agg_its_analysis_qcew_w(memphis_qcew, group = 2, endyear = 2010)
stargazer(broad_agg_its_w[[1]], broad_agg_its_w[[2]], broad_agg_its_w[[3]], 
          title = "Broad Ave. Corridor Interrupted Time Series Estimates (Wage)", 
          column.labels  = c("Retail Wage", "Accomodations Wage", "'Business' Wage"), type = "html")

```