---
title: "Washington DC"
author: "Jamaal Green"
date: "September 4, 2018"
output:
  word_document: default
  pdf_document:
    includes:
      in_header: header.tex
    number_sections: true
fig_width: 7
fig_height: 5
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(cache = TRUE)
```

# 1. Introduction

In order to make their cities more livable, policymakers and planning departments are improving streets and upgrading transportation infrastructure  in order to improve access and mobility for pedestrians and bicyclists through the reduction of on-street parking or traffic lanes. While studies have shown how such upgrades improve safety the question remains whether such infrastructure improvements also improve the economic outcomes of improved corridors. This study will attempt to answer to what extent these types of corridor-level street improvements impact economic activity and business vitality.

DESCRIPTION OF CITY and CITY BIKE NETWORK and HISTORY HERE

[insert city-wide map of DC here]

# 2. Data Sources/Methodology

## 2.1 Data Sources

For this study we used multiple data sources to estimate the effect of new bike lane infrastructure investment. First, we used the Longitudinal Origin-Destination Employment Statistics (LODES) data set from the **Longitudinal Employer-Household Dynamics Dataset** (LEHD).  It integrates existing data from state-supplied administrative records on workers and employers with existing census, surveys, and other administrative records to create a longitudinal data system on U.S employment. This data set tracks Workplace Area Characteristics (WAC), census blocks where people work as opposed to where workers live, for all the census blocks between 2002 and 2015 for most of the states in the US.  As such, LEHD provides geographically granular detail about American’s jobs, workers and local economies, allowing us to examine employment by broad industry sector, wage and educational attainment. Some disadvantages of the LODES data set are that in order to guarantee confidentiality block level data is "fuzzed" so the numbers are not exactly the number of jobs, but they are accurate estimates. Additionally, though we get industrial data, it is only provided at the most general level (the equivalent of two digit NAICS codes) so we are unable to isolate specific retail or service employment such as restaurant workers. That being said, the LODES data set is comprehensive, offers unprecedented geographic detail, and longitudinal allowing for consistent comparisons over time. Unfortunately for Washington DC, though, the city does not have WAC data available to it until 2010, limiting the scope of what we can see with the LODES data.

This report also takes advantage of establishment level **Quarterly Census of Employment and Wages** (QCEW) data. Also referred to as ES-202 data, the QCEW is quarterly data submitted by firms to their respective state governments as part of the unemployment insurance system. Employers report their industry code, their number of employees at the site, and gross pay. The individual QCEW data is confidential and requires special permission from the state in order to use it and has additional data use restrictions. The QCEW gives us address level data on individual establishments as well as detailed employment information. Unfortunately, getting access to such data is difficult and differs for each state and has to be presented in a way to preserve confidentiality. As such, we cannot present ultra-detailed industrial information and have further presentation restrictions depending on the state.

Finally, we also collected **sales tax data**. Sales tax data allows us to estimate a more sensitive measure of economic activity than employment (as the decision to hire or fire for a firm is often an expensive one we expect employment to be a delayed response). Some drawbacks of sales tax data is that some states do not have a sales tax or, in states or cities that do have one, the sales tax data is not broken down by specific industry and it is difficult to accurately parse out accurate figures. But the benefits of sales tax data largely outweigh these issues and do offer a more sensitive metric than employment. 

Washington DC has a general 5.75% sales tax for all businesses with a variety of additional taxes dependent upon use and services rendered. For example, the city imposes a 10% liquor sales tax, a 10% restaurant and rental vehicle tax, and a 14.8% hotel tax. This gives a range of 5.75-20.55% sales tax rates in the city. 

## 2.2 Methodology

We have applied three methods in order to isolate the impact of street improvements while controlling for other economic and regional factors. The methods are an integrated trend analysis (following the NY DOT study), a difference-in-difference approach, and an interrupted time series analysis. 

### 2.2.1 Corridor Comparison Selection

In order to properly isolate the effect of the street improvements we must identify treatment corridors (corridors that actually were improved) and control corridors (corridors that are similar to the treatment corridors except they remain unimproved). Treatment corridors are corridors where new bike or pedestrian related improvements were installed. Ideally, these corridors are made up of a minimum of 10 adjacent, or intersecting, census blocks with a minimal number of retail and accommodations related jobs. Additionally, we will only use corridors where street improvements were installed between 2008 and 2013 in order to guarantee with have sufficient data to track pre and post-treatment employment trends. 

Once corridors are selected based on these criteria we require further testing in order to discern how similar the proposed treatment and control corridors. Finding corridors that are as similar as possible to each other except for the construction of new bicycle/pedestrian infrastructure allows us to approximate true experimental conditions. We will use a combination of descriptive statistics- comparing corridor employment figures to city employment quantiles- and statistical tests- t-tests in order to determine if the average employment in the year before construction of our corridor of interest, by block, for each corridor is similar to the other.

### 2.2.2 Aggregated Trend Comparison

This first method follows the previous NYCDOT study (NYCDOT, 2013), aiming to examine whether the treatment corridors tend to have better business performance than comparison corridors after street improvements. The approach compares the trends of treatment and control corridors in addition to city-wide trends over the full time period we have data for. If treatment corridors show greater increases in employment or sales tax receipts that would represent a positive impact of street improvement on business activities. This method is easy to follow and represents the aggregated trend of business activities. However, it lacks the rigor of econometric estimates and statistical tests that explicitly test whether or not the street improvement caused the change in trend.

### 2.2.3 Difference-in-Difference

The second method aims to estimate the difference in business vitality of pre- and post-improvement periods between improved and comparison corridors within the same time period. This is known as a difference-in-difference (DID) approach. It is a designed to answer the "but for" question of what a corridor's economic trajectory would look like had it streets not been improved.  It requires data from pre/post intervention such as panel data (individual level data overtime) or cross-sectional data (individual or group level). The approach looks at the change in the variable of interest in the treatment group before and after it is treated. In this case this means looking at some time period before and after a street improvement. Meanwhile, the control group has not been treated in either time period. The difference in growth trajectories between the two periods will give an unbiased estimate of the effect of the treatment. DID is a useful technique when randomization on the individual level is not possible. This approach removes biases in the second period comparisons between the treatment group and control group that could be result from permanent differences between those groups, as well as biases from comparisons over time in the treatment group that could be the result of trends. A key assumption of DID estimate is that the differences between control group and treatment group would have remained constant in the absence of treatment. 

DID is a linear modeling approach and its basic formula is expressed as:

$$ Y_{it} = \beta_0 + \beta_1T_{it} + \beta_2A_{it} + \beta_3T_{it}A_{it} +\varepsilon_{it} $$

$Y_{it}$ is the observed outcome in groups i and t (in this case change in employment or sales tax revenue)
$T_{it}$ is a dummy variable set to 1 if the observation is from the treatment group
$A_{it}$ is a dummy variable set to 1 if the observation is from the post treatment period i either groups
$\beta_3$ is the DID estimate of the treatment effect

If the DID estimate $\beta_3$  is significant and positive, then that indicates a positive effect of the street improvement. Conversely if the estimate is significant and negative that indicates a negative effect of the improvement. Finally, a non-significant result indicates the improvement had no statistically discernible effect. 

### 2.2.4 Interrupted Time Series

Interrupted time series is an econometric technique that estimates how street improvements impact corridor economic vitality from a longitudinal perspective. This approach tracks the treatment corridor over time and estimates the impact by the treatment by looking at the change of the corridor growth trend after the treatment. If the treatment has a causal impact, the post-intervention series will have a different level or slope than the pre-intervention series. In our research, interrupted-time series will be used to distinguish differences in growth before and after a specific time break point where an intervention, such as installation of new bicycled facility happens.  

One advantage of ITS is that it allows for the statistical investigation of potential biases in the estimate of the effect of the intervention. Given the longitudinal nature of the test ITS requires a significantly larger amount of data in order to accurately estimate a real effect on the growth trend. 

The interrupted time-series analysis equation can be expressed as: 

$$ Y_t = \beta_0 + \beta_1T_1 + \beta_2X_1 + \beta_3T_1X_1 +\varepsilon_{it} $$

$Y_t$ is the observed business outcome in time period t
$T_t$ indicates the number of quarters from start to finish of the series
$X_t$ is the treatment dummy variable taking values of 0 in the pre-intervention period and 1 in the post-intervention period
$\beta_0$ is the model intercept or baseline level at T = 0
$\beta_1$ represents the change in the outcome with a time unit increase (the pre-intervention trend)
$\beta_2$ is the level change following the intervention
$\beta_3$ indicates the slope change following the intervention 


```{r message=FALSE, warning=FALSE, include=FALSE}

if(!require(pacman)){install.packages("pacman"); library(pacman)}
p_load(here, RPostgreSQL, sf, ggplot2, directlabels,ggthemes, lubridate, dplyr, dbplyr, stargazer,cowplot, zoo)

#query the corridors from bike_lanes
user <- "jamgreen"
host <- "pgsql102.rc.pdx.edu"
pw <- scan(here::here("batteries.pgpss"), what = "")
dbname <- "bike_lanes"

con <- dbConnect("PostgreSQL", host = host, user = user, dbname = dbname, 
                 password = pw, port = 5433)

source(here::here("Code/corridor_comparison_functions.R"))

dc_corridor <- st_read(dsn = con, query = "select a.geoid10 as geoid, a.c000 as c000,
a.cns07 as cns07, a.cns12 as cns12, a.cns14 as cns14, a.cns15 as cns15, 
a.cns16 as cns16, a.cns17 as cns17, a.cns18 as cns18, a.cns19 as cns19, b.st_name as Name, 
b.buildstart as buildstart, b.buildend as buildend, b.sitegroup as corridor_group, b.type as grouptype,  a.year as year, a.geometry as geometry
FROM dc_lehd a, dc_corridors b
WHERE ST_Intersects(ST_Buffer(b.geom, 20), a.geometry);")



#dc_corridor <- st_read(here::here("Data/Indianapolis/dc_corridor_lehd_NAD83.shp"))
dc_corridor <- dc_corridor %>% 
   rename(Type = grouptype) 
#add new colume of construct year as numeric

dc_corridor <- dc_corridor %>%
  rename(C000 = c000, CNS07 = cns07, CNS18 = cns18, CNS12 = cns12, CNS14 = cns14, CNS15 = cns15,CNS16 = cns16, CNS17 = cns17, CNS18 = cns18, CNS19 = cns19, 
         Group = corridor_group, BuildStart = buildstart, BuildEnd = buildend, Name = name)

dc_lehd <- st_read(dsn = con, query = "SELECT * FROM dc_lehd") %>% 
  as.data.frame() %>% 
  rename(C000 = c000, CNS07 = cns07, CNS18 = cns18, CNS12 = cns12, CNS14 = cns14, CNS15 = cns15,
         CNS16 = cns16, CNS17 = cns17, CNS18 = cns18, CNS19 = cns19)

dc_emp_ratio <- employ_ratio_test(dc_corridor)

dc_growth <- growth_rate(dc_corridor)



```

# 3. Corridor Comparisons

Our first test in corridor comparability is comparing the count of the total number, retail, and accommodation jobs within the corridors compared to block figures for the District of Columbia as a whole. This  allows us to have a broad understanding of the relative job density of the corridors. This serves two purposes: first, it gives us a quick estimate of the range of jobs the corridors have; and second, it shows how similar the corridors are to each other in terms of the number of jobs in each. And then, we perform a t-test, a statistical test designed to measure if the means of two different groups are statistically similar. This final test offers us a more rigorous test of the comparability of the corridors. We compare the employment numbers a year before construction for each improvement corridor and its comparison corridor(s). Finally, we illustrate the growth trend of the comparable corridors, and perform a t-test and visual graph to justify the similarity of the corridors in terms of employment change over time. 

Due to the data limitations of the LODES data for Washington DC we can test only the L and M Street corridors as they were completed after 2010. [if and when we get ancillary data we can update this]

## 3.1 L St.

[insert map image here]

Our first treatment corridor is L Street. Constructed in 2012, L runs from 14th to 25th St NW. It's comparator corridors are I and K streets running from 14th to 23rd St Nw. 

### 3.1.1 Corridor Employment Counts

The percentile table shows total, retail, and accommodations employment for L St. compared to I and K Streets based on their percentile ranks of employment compared to the city as a whole. In terms of total and accommodations employment, the corridors are similar in terms of their percentile values, but diverge when it comes to retail employment. 

```{r echo=FALSE, message=FALSE, warning=FALSE}

#comparisons-----

# prepare city level data & block level corridor data at the year before construction
conyear <- first(filter(dc_corridor, Group== 2, Type== "Improvement")$BuildStart)-1 

dc_corridor$Type <- as.character(dc_corridor$Type)
dc_corridor[dc_corridor$Name =="I St",]$Type <- "Control: I St"
dc_corridor[dc_corridor$Name=="K St",]$Type <- "Control: K St"

dc_corridor$Type <- as.factor(dc_corridor$Type)
# find the year before construction


dc_lehd_2011 <- dc_lehd %>% filter(year == conyear, CNS07+ CNS18 > 0)


fifteenth <- dc_corridor %>% filter(Group == 2, Type =="Improvement", year==conyear) %>%  employ_ratio_test(.)

i_st_nw <- dc_corridor %>% filter(Group == 2, Type == "Control: I St", year ==conyear) %>% employ_ratio_test(.)

k_st_nw <- dc_corridor %>% filter(Group == 2, Type == "Control: K St", year ==conyear) %>% employ_ratio_test(.)


# find quantile dataframe 

p <- seq(0,1, by = .05)

quant_df <- data.frame(q_tot_emp = quantile(dc_lehd_2011$C000, 
                                            probs = p, na.rm = TRUE),
                       q_retail = quantile(dc_lehd_2011$CNS07, 
                                           probs = p, na.rm = TRUE),
                       q_food_accom = quantile(dc_lehd_2011$CNS18, 
                                               probs = p, na.rm = TRUE),
                       probs = p)

fifteenth %>% summarise(TotEmp = sum(C000)/nrow(fifteenth), RetailEmp = sum(CNS07)/nrow(fifteenth), AccomEmp = sum(CNS18)/nrow(fifteenth)) %>% as.data.frame()

i_st_nw %>% summarise(TotEmp = sum(C000)/nrow(i_st_nw), RetailEmp = sum(CNS07)/nrow(i_st_nw), AccomEmp = sum(CNS18)/nrow(i_st_nw)) %>% 
  as.data.frame


k_st_nw %>% summarise(TotEmp = sum(C000)/nrow(k_st_nw), RetailEmp = sum(CNS07)/nrow(k_st_nw), AccomEmp = sum(CNS18)/nrow(k_st_nw)) %>% 
  as.data.frame

# t-test: compare retail, food_accom, business amount---
t.test(fifteenth$Business, i_st_nw$Business)
t.test(fifteenth$Retail, i_st_nw$Retail)
t.test(fifteenth$Food_Accom, i_st_nw$Food_Accom)
t.test(fifteenth$ratio1, i_st_nw$ratio1)
t.test(fifteenth$ratio2, i_st_nw$ratio2)

t.test(fifteenth$Business, k_st_nw$Business)
t.test(fifteenth$Retail, k_st_nw$Retail)
t.test(fifteenth$Food_Accom, k_st_nw$Food_Accom)
t.test(fifteenth$ratio1, k_st_nw$ratio1)
t.test(fifteenth$ratio2, k_st_nw$ratio2)

#t-tests growth rates...only two observations, can't run it----

# fifteenth_growth <- dc_growth %>%  
#   mutate(year=as.numeric(as.character(year))) %>% 
#   filter(Group==2, Type=="Improvement", year<=conyear) 
# 
# i_st_growth <- dc_growth %>%  
#   mutate(year=as.numeric(as.character(year))) %>% 
#   filter(Group==2, Type== "Control: I St", year<=conyear) 
# 
# k_st_growth <- dc_growth %>%  
#   mutate(year=as.numeric(as.character(year))) %>% 
#   filter(Group==2, Type== "Control: K St", year<=conyear) 
# 
# 
# t.test(fifteenth_growth$biz_growth,i_st_growth$biz_growth)
# t.test(fifteenth_growth$retail_growth,i_st_growth$retail_growth)
# t.test(fifteenth_growth$food_accom_growth,i_st_growth$food_accom_growth)
# 
# t.test(fifteenth_growth$biz_growth,k_st_growth_growth$biz_growth)
# t.test(fifteenth_growth$retail_growth,k_st_growth_growth$retail_growth)
# t.test(fifteenth_growth$food_accom_growth,k_st_growth_growth$food_accom_growth)


```


 

| Corridor | Tot Emp | Retail Emp | Accom Emp | Tot (%) | Retail (%) | Accom (%) |
|----------|---------|------------|-----------|---------|------------|-----------|
| L St.    | 2188    | 39         | 213       | 90-95   | 90-95      | 95-100    |
| I St.    | 1295    | 4          | 103       | 85-90   | 60-65      | 85-90     |
| K St.    | 1804    | 15         | 167       | 90-95   | 80-85      | 90-95     |

Table 1:  L, I and K St. Employment Percentiles, 2011 employment numbers

### 3.1.2 Corridor Average Employment Comparisons

We performed t-tests on three metrics at the census block level: "business" employment, the sum of retail and accommodations employment; a "business share" metric that is the share of employment in a census block of business employment over the sum of other services industries such as professional/scientific services, public administration and educational services; finally, a second business share metric on a smaller share of services employment including professional/scientific services, administrative/waste management services and arts/accommodation services (check appendix for variable definitions).

The t-test did return one significant result on the difference between L and I street retail employment. This means that the two streets may not be directly comparable for retail, but on all other metrics the t-tests were non-significant. Since the corridors have similar concentrations of employment across our sectors of interest, and largely have non-significant differences in their average employment this means that the corridors are comparable and are appropriate for continued testing.

## 3.2 M St.

[insert map image here]

The M St. corridor was constructed in 2014 and runs parallel to the L St. corridor. M St.'s comparator corridors are also I and K St.

### 3.2.1 Corridor Employment Counts

The percentile table shows total, retail, and accommodations employment for M St. compared to I and K Streets based on their percentile ranks of employment compared to the city as a whole. In terms of total and accommodations employment, the corridors are similar in terms of their percentile values, but diverge when it comes to retail employment. 

```{r echo=FALSE, message=FALSE, warning=FALSE}

#comparisons-----

# prepare city level data & block level corridor data at the year before construction
conyear <- first(filter(dc_corridor, Group== 5, Type== "Improvement")$BuildStart)-1 

dc_corridor$Type <- as.character(dc_corridor$Type)
dc_corridor[dc_corridor$Name =="I St",]$Type <- "Control: I St"
dc_corridor[dc_corridor$Name=="K St",]$Type <- "Control: K St"

dc_corridor$Type <- as.factor(dc_corridor$Type)
# find the year before construction


dc_lehd_2013 <- dc_lehd %>% filter(year == conyear, CNS07+ CNS18 > 0)


m_st <- dc_corridor %>% filter(Group == 5, Type =="Improvement", year==conyear) %>%  employ_ratio_test(.)

i_st_nw <- dc_corridor %>% filter(Group == 5, Type == "Control: I St", year ==conyear) %>% employ_ratio_test(.)

k_st_nw <- dc_corridor %>% filter(Group == 5, Type == "Control: K St", year ==conyear) %>% employ_ratio_test(.)


# find quantile dataframe 

p <- seq(0,1, by = .05)

quant_df <- data.frame(q_tot_emp = quantile(dc_lehd_2013$C000, 
                                            probs = p, na.rm = TRUE),
                       q_retail = quantile(dc_lehd_2013$CNS07, 
                                           probs = p, na.rm = TRUE),
                       q_food_accom = quantile(dc_lehd_2013$CNS18, 
                                               probs = p, na.rm = TRUE),
                       probs = p)

m_st %>% summarise(TotEmp = sum(C000)/nrow(fifteenth), RetailEmp = sum(CNS07)/nrow(fifteenth), AccomEmp = sum(CNS18)/nrow(fifteenth)) %>% as.data.frame()

i_st_nw %>% summarise(TotEmp = sum(C000)/nrow(i_st_nw), RetailEmp = sum(CNS07)/nrow(i_st_nw), AccomEmp = sum(CNS18)/nrow(i_st_nw)) %>% 
  as.data.frame


k_st_nw %>% summarise(TotEmp = sum(C000)/nrow(k_st_nw), RetailEmp = sum(CNS07)/nrow(k_st_nw), AccomEmp = sum(CNS18)/nrow(k_st_nw)) %>% 
  as.data.frame

# t-test: compare retail, food_accom, business amount---
t.test(m_st$Business, i_st_nw$Business)
t.test(m_st$Retail, i_st_nw$Retail)
t.test(m_st$Food_Accom, i_st_nw$Food_Accom)
t.test(m_st$ratio1, i_st_nw$ratio1)
t.test(m_st$ratio2, i_st_nw$ratio2)

t.test(m_st$Business, k_st_nw$Business)
t.test(m_st$Retail, k_st_nw$Retail)
t.test(m_st$Food_Accom, k_st_nw$Food_Accom)
t.test(m_st$ratio1, k_st_nw$ratio1)
t.test(m_st$ratio2, k_st_nw$ratio2)

#t-tests growth rates...only two observations, can't run it----

# fifteenth_growth <- dc_growth %>%  
#   mutate(year=as.numeric(as.character(year))) %>% 
#   filter(Group==2, Type=="Improvement", year<=conyear) 
# 
# i_st_growth <- dc_growth %>%  
#   mutate(year=as.numeric(as.character(year))) %>% 
#   filter(Group==2, Type== "Control: I St", year<=conyear) 
# 
# k_st_growth <- dc_growth %>%  
#   mutate(year=as.numeric(as.character(year))) %>% 
#   filter(Group==2, Type== "Control: K St", year<=conyear) 
# 
# 
# t.test(fifteenth_growth$biz_growth,i_st_growth$biz_growth)
# t.test(fifteenth_growth$retail_growth,i_st_growth$retail_growth)
# t.test(fifteenth_growth$food_accom_growth,i_st_growth$food_accom_growth)
# 
# t.test(fifteenth_growth$biz_growth,k_st_growth_growth$biz_growth)
# t.test(fifteenth_growth$retail_growth,k_st_growth_growth$retail_growth)
# t.test(fifteenth_growth$food_accom_growth,k_st_growth_growth$food_accom_growth)


```

| Corridor | Tot Emp | Retail Emp | Accom Emp | Tot (%) | Retail (%) | Accom (%) |
|----------|---------|------------|-----------|---------|------------|-----------|
| 15th St. | 2188    | 39         | 213       | 90-95   | 90-95      | 95-100    |
| I St.    | 1295    | 4          | 103       | 85-90   | 60-65      | 85-90     |
| K St.    | 1804    | 15         | 167       | 90-95   | 80-85      | 90-95     |

Table 2: M, I and K St. Employment Percentiles, 2013 employment numbers

### 3.2.2 Corridor Average Employment Comparisons

The t-test did return one significant result on the difference between M and I street average retail employment. This means that the two streets may not be directly comparable for retail, but on all other metrics the t-tests were non-significant. Since the corridors have similar concentrations of employment across our sectors of interest, and largely have non-significant differences in their average employment this means that the corridors are comparable and are appropriate for continued testing.

# 4. Data Analysis

## 4.1  L St.

### 4.1.1 Trend Analysis

#### LEHD


```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width = 9, fig.asp=.5}


#L St index table and plot
l_st_agg_idx <- agg_index_trend_table(dc_corridor, group = 2, construct_year = 2012)

#city agg plots

dc_agg <- city_agg_index_trend_table(dc_lehd, construct_year = 2012)

l_st_agg_idx <- bind_rows(l_st_agg_idx, dc_agg)
l_st_agg_idx <- l_st_agg_idx %>% filter(!is.na(year))



# riverside_agg_idx <- riverside_agg_idx %>% 
#   mutate(Type = case_when(Type == "improvement" ~ "Treatment",
#                           Type == "control" ~ "Control: Cedar Ave.",
#                           Type == "city" ~ "City"))
# 
# riverside_agg_idx$Type <- factor(riverside_agg_idx$Type, levels = c("Treatment", "Control: Cedar Ave.", "City"))


# construct_year <- 2009
# end_year <- 2010
# 
# construct_date <- as.character(paste0(construct_year, "-01-01"))
# construct_date <- as.Date(construct_date, "%Y-%m-%d")
#   
#   
# end_date <- as.character(paste0(end_year, "-01-01"))
# end_date <- as.Date(end_date, "%Y-%m-%d")

l_agg_retail <- city_agg_index_trend_one_control_plot(l_st_agg_idx, industry = "Retail", corridor_name = "Riverside Ave.", control_corridor = "Cedar Ave.", industry_code = "CNS07_sd", construct_year = 2009, end_year = 2010)

riverside_agg_accom <- city_agg_index_trend_one_control_plot(riverside_agg_idx, industry = "Accommodations", corridor_name = "Riverside Ave.", control_corridor = "Cedar Ave.", industry_code = "CNS07_sd", construct_year = 2009, end_year = 2010)


plot_grid(riverside_agg_retail, riverside_agg_accom, align = "h")

```

