---
title: "minneapolis models"
author: "Jamaal Green"
date: "May 29, 2018"
output: html_document
---

#minneapolis model outputs...DiD and ITS

```{r, echo=FALSE, results='asis'}

if(!require(pacman)){install.packages("pacman"); library(pacman)}
<<<<<<< HEAD
p_load(here, RPostgreSQL, sf, tidyr, ggplot2, ggthemes, dplyr, dbplyr, stargazer,cowplot)
=======
p_load(here, RPostgreSQL, sf, tidyr, ggplot2, ggthemes, dplyr, dbplyr, stargazer,cowplot, lubridate, zoo)

>>>>>>> ca96e0fe213d8c8a684af900c043e54958e3fb3f
source(here::here("Code/corridor_comparison_functions.R"))

#query the corridors from bike_lanes
user <- "jamgreen"
host <- "pgsql102.rc.pdx.edu"
pw <- scan(here::here("batteries.pgpss"), what = "")
dbname <- "bike_lanes"

con <- dbConnect("PostgreSQL", host = host, user = user, dbname = dbname, 
                 password = pw, port = 5433)

minn_corridor <- st_read(dsn = con, query = "select a.geoid10 as geoid, a.c000 as c000,
a.cns07 as cns07, a.cns18 as cns18, a.cns12 as cns12, a.cns14 as cns14, a.cns15 as cns15, 
a.cns16 as cns16, a.cns17 as cns17, a.cns18 as cns18, a.cns19 as cns19, b.name as Name, 
b.buildstart as buildstart, b.buildend as buildend, b.group as corridor_group, 
b.type as grouptype,  a.year as year, a.geometry as geometry
FROM minneapolis_lehd a, minneapolis_corridors b
WHERE ST_Intersects(ST_Buffer(b.geom, 20), a.geometry);")

names(minn_corridor) <- toupper(names(minn_corridor)) 

minn_corridor <- minn_corridor %>% rename(Type = GROUPTYPE, year = YEAR, Group = CORRIDOR_GROUP)

# minn_corridor <- st_read(here::here("Data/minneapolis/minn_corridor_lehd_wgs84.geojson"))

#riverside

riverside_agg_did <- did_agg_analysis(df_did = minn_corridor, group = 1, endyear = 2009)
stargazer(riverside_agg_did[[1]], riverside_agg_did[[2]], riverside_agg_did[[3]], 
          title = "Riverside Corridor Difference-in-Difference Estimates", 
          column.labels  = c("Retail Emp.", "Accomodations Emp.", "'Business' Emp."), type = "html")

riverside_agg_its <- agg_its_analysis(df_its = minn_corridor, group = 1, endyear = 2009)
stargazer(riverside_agg_its[[1]], riverside_agg_its[[2]], riverside_agg_its[[3]], type = "html", 
          title = "Interrupted Time Series- Riverside Ave.", 
          column.labels  = c("Retail Emp.", "Accomodations Emp.", "'Business' Emp."))

#franklin
franklin_agg_did <- did_agg_analysis(df_did = minn_corridor, group = 2, endyear = 2011)
stargazer(franklin_agg_did[[1]], franklin_agg_did[[2]],franklin_agg_did[[3]],         title = "Franklin Ave. Corridor Difference-in-Difference Estimates", 
          column.labels  = 
            c("Retail Emp.", "Accomodations Emp.", "'Business' Emp."), 
          type = "html")


franklin_its <- agg_its_analysis(df_its = minn_corridor,  group = 2, endyear = 2011)
stargazer(franklin_its[[1]], franklin_its[[2]], franklin_its[[3]], 
          type = "html", title = "Interrupted Time Series- Franklin Ave.", 
          column.labels = c("Retail Emp.", "Accommodations Emp.", "'Business' Emp."))

#central
 

central_did <- did_agg_analysis(df_did = minn_corridor, group = 3, endyear = 2012)
stargazer(central_did[[1]], central_did[[2]], central_did[[3]], 
          title = "Central Ave. Corridor Difference-in-Difference Estimates", 
          column.labels  = c("Retail Emp.", "Accomodations Emp.", "'Business' Emp."), type = "html")

central_its <- agg_its_analysis(df_its = minn_corridor, group = 3, endyear = 2012)
stargazer(central_its[[1]], central_its[[2]], central_its[[3]], 
          type = "html", title = "Interrupted Time Series- Central Ave.", 
          column.labels = c("Retail Emp.", "Accommodations Emp.", "'Business' Emp."))

#lyndale

lyndale_did <- did_agg_analysis(df_did = minn_corridor, group = 4, endyear = 2009)
stargazer(lyndale_did[[1]], lyndale_did[[2]], lyndale_did[[3]], 
          title = "Lyndale Ave. Corridor Difference-in-Difference Estimates", 
          column.labels  = c("Retail Emp.", "Accomodations Emp.", "'Business' Emp."), type = "html")

lyndale_its <- agg_its_analysis(minn_corridor, group = 4, endyear = 2009)
stargazer(lyndale_its[[1]], lyndale_its[[2]], lyndale_its[[3]], 
          type = "html", title = "Interrupted Time Series- Lyndale Ave.", 
          column.labels = c("Retail Emp.", "Accommodations Emp.", "'Business' Emp."))

#north 2nd


north_did <- did_agg_analysis(df_did = minn_corridor, group = 5, endyear = 2011)
stargazer(north_did[[1]], north_did[[2]], north_did[[3]], 
          title = "North Second St.Corridor Difference-in-Difference Estimates", 
          column.labels  = c("Retail Emp.", "Accomodations Emp.", "'Business' Emp."), type = "html")

north_its <- agg_its_analysis( minn_corridor, group = 5, endyear = 2011)
stargazer(north_its[[1]], north_its[[2]], north_its[[3]], type = "html",
         title = "Interrupted Time Series- North 2nd Ave.", 
          column.labels = c("Retail Emp.", "Accommodations Emp.", "'Business' Emp.") )


# sales tax models-----------------------------------


minn_sale <- tbl(con, "minn_sales_tax")
minn_sale <- collect(minn_sale)

minn_sale$Type <- stringr::str_trim(minn_sale$Type, side = "both")

#riverside

riverside_sale <- minn_sale %>% filter(Group == 1) %>% 
  mutate(pre_post = if_else(year >= 2009, 1, 0))

riverside_did_rest <- lm(Restaurant ~ Type + pre_post + Type*pre_post, data = riverside_sale)
riverside_did_retail <- lm(Retail ~ Type + pre_post + Type*pre_post, data = riverside_sale)

stargazer(riverside_did_rest, riverside_did_retail, type = "html",
         title = "Riverside Ave. Sales Tax Difference-in-Difference Estimates", 
          column.labels = c("Restaurant Sales", "Retail Sales") )

riverside_its <- riverside_sale %>% filter(Type == "Improvement") %>% 
  mutate(ts_year = year - 2003)

riverside_its_rest <- lm(Restaurant ~ ts_year + pre_post + ts_year*pre_post, data = riverside_its)
riverside_its_retail <- lm(Retail ~ ts_year + pre_post + ts_year*pre_post, data = riverside_its)

stargazer(riverside_its_rest, riverside_its_retail, type = "html",
         title = "Riverside Ave. Sales Tax ITS Estimates", 
          column.labels = c("Restaurant Sales", "Retail Sales"))

#franklin...only doing ITS

franklin_its <- minn_sale %>% filter(Group == 2, Type == "Improvement") %>% 
  mutate(pre_post = if_else(year >= 2011, 1, 0), ts_year = year - 2003)

franklin_its_rest <- lm(Restaurant ~ ts_year + pre_post + ts_year*pre_post, data = franklin_its)
franklin_its_retail <- lm(Retail ~ ts_year + pre_post + ts_year*pre_post, data = franklin_its)

stargazer(franklin_its_rest, franklin_its_retail, type = "html",
         title = "Franklin Ave. Sales Tax ITS Estimates", 
          column.labels = c("Restaurant Sales", "Retail Sales"))
  

#central

central_sale <- minn_sale %>% filter(Group == 3) %>% 
  mutate(pre_post = if_else(year >= 2012, 1, 0))

central_did_rest <- lm(Restaurant ~ Type + pre_post + Type*pre_post, data = central_sale)
central_did_retail <- lm(Retail ~ Type + pre_post + Type*pre_post, data = central_sale)

stargazer(central_did_rest, central_did_retail, type = "html",
         title = "Central Ave. Sales Tax Difference-in-Difference Estimates", 
          column.labels = c("Restaurant Sales", "Retail Sales") )

central_its <- central_sale %>% filter(Type == "Improvement") %>% 
  mutate(ts_year = year - 2003)

central_its_rest <- lm(Restaurant ~ ts_year + pre_post + ts_year*pre_post, data = central_its)
central_its_retail <- lm(Retail ~ ts_year + pre_post + ts_year*pre_post, data = central_its)

stargazer(central_its_rest, central_its_retail, type = "html",
         title = "Central Ave. Sales Tax ITS Estimates", 
          column.labels = c("Restaurant Sales", "Retail Sales"))

#lyndale

lyndale_sale <- minn_sale %>% filter(Group == 4) %>% 
  mutate(pre_post = if_else(year >= 2009, 1, 0))

lyndale_did_rest <- lm(Restaurant ~ Type + pre_post + Type*pre_post, data = lyndale_sale)
lyndale_did_retail <- lm(Retail ~ Type + pre_post + Type*pre_post, data = lyndale_sale)

stargazer(lyndale_did_rest, lyndale_did_retail, type = "html",
         title = "Lyndale Ave. S. Sales Tax Difference-in-Difference Estimates", 
          column.labels = c("Restaurant Sales", "Retail Sales") )

lyndale_its <- lyndale_sale %>% filter(Type == "Improvement") %>% 
  mutate(ts_year = year - 2003)

lyndale_its_rest <- lm(Restaurant ~ ts_year + pre_post + ts_year*pre_post, data = lyndale_its)
lyndale_its_retail <- lm(Retail ~ ts_year + pre_post + ts_year*pre_post, data = lyndale_its)

stargazer(lyndale_its_rest, lyndale_its_retail, type = "html",
         title = "Lyndale Ave. S. Sales Tax ITS Estimates", 
          column.labels = c("Restaurant Sales", "Retail Sales")) 

#2nd street....ITS only for restaurant because too many missing DID terms

second_sale <- minn_sale %>% filter(Group == 5) %>% 
  mutate(pre_post = if_else(year >= 2011, 1, 0))

second_did_retail <- lm(Retail ~ Type + pre_post + Type*pre_post, data = second_sale)

stargazer(second_did_retail, type = "html",
         title = "North 2nd Sales Tax Difference-in-Difference Estimates", 
          column.labels = c("Retail Sales")) 

second_sale <- minn_sale %>% filter(Group == 5, Type == "Improvement") %>% 
  mutate(pre_post = if_else(year >= 2011, 1, 0), ts_year = year - 2003)
  

second_its_retail <- lm(Retail ~ ts_year + pre_post + ts_year*pre_post, data = second_sale)

stargazer(second_its_retail, type = "html",
         title = "North 2nd Sales Tax ITS Estimates", 
          column.labels = c("Retail Sales"))  

<<<<<<< HEAD
dbDisconnect(con)

```
=======


# qcew models-----------------------

#riverside did

minn_qcew <- tbl(con, "minneapolis_qcew_modified")

riverside_qcew <- minn_qcew %>% filter(corridors == "Riverside Ave" | corridors == "Cedar Ave")

riverside_qcew <- collect(riverside_qcew) %>% 
  mutate(year_quarter = paste0(year,"-",quarter), 
          year_quarter = as.yearqtr(year_quarter))

riverside_qcew <- riverside_qcew %>% 
  mutate(street_type = case_when(street_type == "improvement" ~ "Treatment",
                                 street_type == "control" ~ "Control: Cedar Ave"))

riverside_qcew$street_type <- factor(riverside_qcew$street_type, 
                                     levels = c("Treatment", "Control: Cedar Ave"))

riverside_qcew <- riverside_qcew %>% 
  mutate(pre_post = if_else(year_quarter >= "2009 Q1", 1, 0))

river_qcew_did_emp <- lm(avg_emp ~ street_type + pre_post + street_type*pre_post, riverside_qcew)
river_qcew_did_wages <- lm(total_wages ~ street_type + pre_post + street_type*pre_post, riverside_qcew)

river_qcew_did_list <- list(river_qcew_did_emp, river_qcew_did_wages)

stargazer(river_qcew_did_list[[1]], river_qcew_did_list[[2]],
          title = "Riverside Avenue QCEW Difference-in-Difference Estimates",
          column.labels = c("Average Employment", "Total Wages"), type = "html")

#riverside ITS

river_its <- riverside_qcew %>% 
  filter(street_type == "Treatment") %>% 
  group_by(year) %>% summarise(avg_emp = mean(avg_emp, na.rm = TRUE),
                               tot_wages = sum(total_wages, na.rm = TRUE)) %>% 
  mutate(ts_year = year - 2000, pre_post = if_else(year >= 2009, 1, 0))

river_qcew_its_emp <- lm(avg_emp ~ ts_year + pre_post + ts_year*pre_post, 
                         data = river_its)

river_qcew_its_wages <- lm(tot_wages ~ ts_year + pre_post + ts_year*pre_post, 
                         data = river_its)

river_qc_its_list <- list(river_qcew_its_emp, river_qcew_its_wages)

stargazer(river_qc_its_list[[1]], river_qc_its_list[[2]],
          title = "Riverside Avenue QCEW ITS Estimates",
          column.labels = c("Average Employment", "Total Wages"), type = "html")

#franklin ITS

franklin_its <- minn_qcew %>% 
  filter(corridors == "Franklin Ave", street_type == "improvement") %>% 
    group_by(year) %>% 
  summarise(avg_emp = mean(avg_emp, na.rm = TRUE),
            tot_wages = sum(total_wages, na.rm = TRUE)) %>% 
  mutate(ts_year = year - 2000, pre_post = if_else(year >= 2011, 1, 0)) %>% 
  collect()


franklin_qcew_its_emp <- lm(avg_emp ~ ts_year + pre_post + ts_year*pre_post,
                            data = franklin_its)

franklin_qcew_its_wage <- lm(tot_wages ~ ts_year + pre_post + ts_year*pre_post,
                            data = franklin_its)

franklin_qcew_list <- list(franklin_qcew_its_emp, franklin_qcew_its_wage)

stargazer(franklin_qcew_list[[1]], franklin_qcew_list[[2]], title = "Franklin Ave ITS Estimates", column.labels = c("Average Employment", "Total Wages"), type = "html")

#central DiD

central_qcew <- minn_qcew %>% 
  filter(corridors == "Central Ave" | corridors == "University Ave")

central_qcew <- collect(central_qcew) %>% 
  mutate(year_quarter = paste0(year,"-",quarter), 
          year_quarter = as.yearqtr(year_quarter))

central_qcew <- central_qcew %>% 
  mutate(street_type = case_when(street_type == "improvement" ~ "Treatment",
                                 street_type == "control" ~ "Control: University Ave"))

central_qcew$street_type <- factor(central_qcew$street_type, 
                                     levels = c("Treatment", "Control: University Ave"))

central_qcew <- central_qcew %>% 
 mutate(pre_post = if_else(year_quarter >= "2012 Q1", 1, 0)) 

central_qc_emp_did <- lm(avg_emp ~ pre_post + street_type + pre_post*street_type, data = central_qcew)
central_qc_wages_did <- lm(total_wages ~ pre_post + street_type + pre_post*street_type, 
                           data = central_qcew)

central_qc_did_list <- list(central_qc_emp_did, central_qc_wages_did)

stargazer(central_qc_did_list[[1]], central_qc_did_list[[2]], title = "Central Ave. QCEW Difference-in-Difference Estimates", column.labels = c("Average Employment", "Total Wages"), type = "html")

#central ITS

central_its <- central_qcew %>% 
  filter(street_type == "Treatment")

central_its <- central_its %>% 
  group_by(year) %>% 
  summarise(avg_emp = mean(avg_emp, na.rm = TRUE),
            tot_wages = sum(total_wages, na.rm = TRUE)) %>% 
  mutate(ts_year = year - 2000, pre_post = if_else(year >= 2012, 1, 0))

central_qcew_its_emp <- lm(avg_emp ~ ts_year + pre_post + ts_year*pre_post, data = central_its)
central_qcew_its_wages <- lm(tot_wages ~ ts_year + pre_post + ts_year*pre_post, data = central_its)

central_qcew_its_list <- list(central_qcew_its_emp, central_qcew_its_wages)

stargazer(central_qcew_its_list[[1]], central_qcew_its_list[[2]], title = "Central Ave QCEW ITS Estimates", column.labels = c("Average Employment", "Total Wages"), type = "html")

#lyndale ave DiD

lyndale_qcew <- minn_qcew %>% 
  filter(corridors == "Lyndale Ave S" | corridors == "Grand Ave")

lyndale_qcew <- collect(lyndale_qcew) %>% 
  mutate(year_quarter = paste0(year,"-",quarter), 
          year_quarter = as.yearqtr(year_quarter))

lyndale_qcew <- lyndale_qcew %>% 
  mutate(street_type = case_when(street_type == "improvement" ~ "Treatment",
                                 street_type == "control" ~ "Control: Grand Ave"))

lyndale_qcew$street_type <- factor(lyndale_qcew$street_type, 
                                     levels = c("Treatment", "Control: Grand Ave"))

lyndale_qcew <- lyndale_qcew %>% 
  mutate(pre_post = if_else(year_quarter >= "2008 Q1"))

```

```{r message=FALSE, warning=FALSE, include=FALSE}
dbDisconnect(con)

```

>>>>>>> ca96e0fe213d8c8a684af900c043e54958e3fb3f
